### 2015-05-15 whoop.tex
update

\noindent\textbf{Verification and Error Reporting }
%
For each pair of entry points, the instrumented sequential program, equipped with procedure and loop summaries, is sent to the Boogie verification engine. Boogie generates a VC, for each procedure in the program, and discharges it to the Z3 theorem prover.  In particular, the verification for the root-level procedure, encoding the sequential program sketched in Figure~\ref{fig:sequentialization}, encodes the race-freedom check for the entry point pair. Successful verification implies that the entry point pair is free of data races, while an error (i.e.\ counterexample) denotes a \emph{potential} data race and is reported to the user. To improve usability, \whoop has a built-in error reporter that matches counterexamples to source code. The following is a race that \whoop found and reported for the example of Figure~\ref{fig:data_race_example}:

>>>>

\noindent\textbf{Verification and Error Reporting }
%
For each entry point pair, the instrumented sequential program, equipped with procedure and loop summaries, is sent to the Boogie verification engine. For each procedure in the program, Boogie generates a VC and discharges it to the Z3 theorem prover.  In particular, the verification for the root-level procedure, encoding the sequential program sketched in Figure~\ref{fig:sequentialization}, encodes the race-freedom check for the entry point pair. Successful verification implies that the pair is race-free, while an error (i.e.\ counterexample) denotes a \emph{potential} data race and is reported to the user. To improve usability, \whoop has a built-in error reporter that matches counterexamples to source code. The following is a race that \whoop found and reported for the example of Figure~\ref{fig:data_race_example}:
